---
title: "exploratory_analysis"
author: "Tim Mastny"
date: "March 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
d <- read_csv(here("train.csv"))
d
```

Total order

```{r}
table(d$order)
```


Grouping by session id

```{r}
d %>%
  group_by(sessionID) %>%
  count(order) %>% 
  ungroup() %>%
  count(order)
```

cart steps and order

```{r}
d %>%
  group_by(cartStep) %>%
  count(order)
```

So we would like to include it as a predictor.

The question is, how do you work with conditional data, rather than missing data?

```{r}
d
```

```{r}
unique(d$availability)
```


Some values are actually missing?

```{r}
d %>%
  filter(sessionID == 2)
```



## What to predict

Note that while our data is serialized, with multiple sessionIDs, our final prediction should be grouped on session id.

Idea: create a new feature that is a count of the number of session IDs present.

Note that there are many session IDs with many observations.

```{r}
table(d$sessionID)[table(d$sessionID) > 75]
```

```{r}
d %>%
  filter(sessionID == 1130)
```

This is a good example, where the final observation of the session contains the final cart step, etc. Need a way to aggregate features into final step. 

Note that there is an inherent ordering in the session observations, so it might make sense to just remove all but the last one. 

## How to subset data

```{r}
ud <- d %>%
  group_by(sessionID) %>%
  mutate(row_id = row_number()) %>%
  mutate(session_nums = max(row_id)) %>%
  filter(row_id == max(row_id)) %>%
  ungroup() %>%
  select(-row_id)
```



## Timeline of orders

Let's look at the orders over time. For this it also makes sense to clean the data in that manner.

```{r}
unique(d$hour)
unique(d$weekday)
```

```{r}
library(lubridate)
hours(23)
days(5)
hours(6) + days(5)
```

```{r}
# this doesn't group_by correctly. Let's use dates instead. 
ud %>%
  mutate(time = hours(hour) + days(weekday)) %>%
  select(sessionID, time, order)
```

```{r}
ses_date <- ymd("1999/1/1")
ses_date
hour(ses_date) <- 1
day(ses_date) <- 5
ses_date
```

```{r}
dater <- function(new_hours, new_day) {
  fake_date <- ymd("1999/1/1")
  hour(fake_date) <- new_hours
  day(fake_date) <- new_day
  as.POSIXct(fake_date)
}

ud %>%
  mutate(time = dater(hour, weekday)) %>%
  select(sessionID, time)
```
```{r}
orders <- ud %>%
  mutate(time = dater(hour, weekday)) %>% 
  group_by(time, order) %>%
  summarise(orders = n()) %>%
  group_by(time)
```

```{r}
ggplot(orders, aes(x = time, y = orders, group = order, color = order)) +
  geom_line() +
  geom_smooth()
```












