---
title: "NA Explorer"
author: "Tim Mastny"
date: "March 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
library(lubridate)
library(tidyverse)
library(here)

d <- read_csv(here("train.csv"))

source(here("R", "cleaners.R"))
```

In the previous explorer, we noticed that we need a max argument. Since then, I've updated `unique_sessioner` to accomdate this information:

```{r}
ud <- d %>%
  unique_sessioner()
```

```{r}
ud
```

## Fixing NAs

Can we replace some NAs with zeros?

```{r}
ud %>%
  select_if(~any(is.na(.)) & is.double(.))
```

```{r}
ud %>%
  select_if(~any(is.na(.)) & is.double(.)) %>%
  summarise_all(min, na.rm = TRUE)
```

So there are instances where doubles are zero, but not NA. Why?

```{r}
ud %>%
  filter(clickMin == 0)
```

Somehow we have an example where an item was added to the cart (clickCount == 1), but there is no click min or max

```{r}
ud %>%
  filter(is.na(clickMin))
```

```{r}
ud %>%
  filter(sessionID == 66)
```

This means I may need to do conditional impute. If the item was sold, can we impute clickMin? Otherwise, zero?

This is not quite possible: `recipes` give an option to impute only certain columns of the data, but not for certain row values.

```{r}
d %>%
  filter(sessionID == 66)
```

## Observation

If `clickMin` is NA, so are all the other click attributes

```{r}
ud %>%
  filter_if(is.double, any_vars(is.na(.)))
```















