---
title: "Impute with Recipes"
author: "Tim Mastny"
date: "March 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(lubridate)
library(tidyverse)
library(here)

d <- read_csv(here("data", "train.csv"))

source(here("R", "cleaners.R"))
```


```{r}
ud <- d %>%
  unique_sessioner()
```


Let's test out various ways to impute missing data.



## Dummy

Dummifying `availability` might help to deal with those NAs. They indictor variable there will be zero for every category. 

```{r}
library(recipes)
rec_obj <- recipe(order ~ ., data = ud) %>%
  step_modeimpute(availability) %>%
  step_dummy(availability) %>%
  prep(training = ud)
```

```{r}
training <- bake(rec_obj, newdata = ud)
training
```

```{r}
table(ud$availability, exclude = NULL)
```

```{r}
rec_obj2 <- recipe(order ~ ., data = ud) %>%
  step_knnimpute(availability) %>%
  step_dummy(availability) %>%
  prep(training = ud)
```

```{r}
training2 <- bake(rec_obj, newdata = ud)
training2
```

```{r}
any(is.na(ud$cartStep))
```

## Doubles

Time: roughly 30 minutes

```{r}
library(recipes)
rec_obj <- recipe(order ~ ., data = ud) %>%
  step_bagimpute(-all_nominal()) %>%
  step_modeimpute(all_nominal()) %>%
  prep(training = ud)
```

Gives following error:

> Error in gower_work(x = x, y = y, pair_x = pair_x, pair_y = pair_y, n = n, : STRING_ELT() can only be applied to a 'character vector', not a 'integer'

```{r}
training <- bake(rec_obj, newdata = ud)
training
```

```{r}
tidy(rec_obj)
```

Awesome! Bag impute seems to work!

```{r}
nrow(training %>% na.omit())
```

```{r}
any(is.na(ud$order))
```

Try all with bagged. Might be better for `integer` types.

```{r}
rec_obj3 <- recipe(order ~ ., data = ud) %>%
  step_bagimpute(all_predictors()) %>%
  prep(training = ud)
```

```{r}
training3 <- bake(rec_obj3, newdata = ud)
training3
```

## list of steps

Send list of steps to cooking function to process data in purrr loop.

## Customer id

Note that we probability shouldn't impute costumer id. Create a unique value for each missing observation.

```{r}
length(unique(ud$customerID))
```

```{r}
length(ud$customerID[is.na(ud$customerID)])
```

Should customer ID be a factor? Maybe make all NAs 0?

```{r}
min(ud$customerID, na.rm = TRUE)
```

## NAs


```{r}
training
```

```{r}
training %>%
  fix_customerid() %>%
  filter(is.na(customerID))
```


```{r}
library(recipes)
rec <- recipe(order ~ ., data = training) %>%
  step_modeimpute(status, availability) %>%
  prep(training = training)

dat <- bake(rec, newdata = training)
dat
```

```{r}
a <- map_lgl(dat, ~any(is.na(.)))
a[a]
```

```{r}
a <- map_lgl(train, ~any(is.na(.)))
a[a]
```
```{r}
a <- map_lgl(training, ~any(is.na(.)))
a[a]
```
```{r}
training %>%
  filter(is.na(customerID))
```

```{r}
train %>%
  filter(is.na(customerID)) 
```



